Analyses

### 2021-11-05 analyses.RmD
- implemented feedback from Nick - updated analyses - provided additional plots for control variables

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 120)
```

@@

# define packages
packages <- c("corrplot", "devtools", "GGally", "ggplot2", "gridExtra", "haven", "kableExtra", "knitr", 
              "lavaan", "lme4", "magrittr", "mice", "MVN", "PerFit", "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse")

@@

@@

```{r}
make_graph <- function(model, title, ll, ul, line = FALSE, labels = FALSE){
  dat <- coefficients(model)$wave %>% 
    tibble::rownames_to_column("wave") %>% 
    rename(value = "(Intercept)") %>% 
    mutate(wave = as.integer(.$wave),
           value = as.numeric(.$value))

  graph <- 
    ggplot(dat, aes(wave, value)) +
    theme_bw() +
    theme(text = element_text(size = 8)) + 
    geom_bar(data = dat, aes(wave, value), stat = "identity") +
    coord_cartesian(ylim = c(ll, ul)) +
    ggtitle(title)

  if(line) {graph <- graph + 
    geom_smooth(se = FALSE, method = 'loess', size = 1.5)}

  if(labels) {graph <- graph +
    geom_text(aes(label = round(value, 2)), hjust = 1.2, color = "white",
              fontface = "bold", angle = 90)
  }

  graph
}
```

@@

```{r}
make_graph_res <- function(data){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                lwd = .75, height = .2
                , position = position_dodge(.6)
                ) +
  geom_point(size = 2
             , position = position_dodge(.6)
             ) +
  geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed") + 
    geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed") + 
  geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed") + 
    geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed") + 
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free") 
}
```

@@

```{r}
doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
# d_raw <- read_spss("data/10094_da_de_v4_0.zsav")
d_raw <- read_csv("data/10094_da_de_v4_0.csv")
```

@@

```{r}
d_wide %<>%
  mutate_at(vars(everything(.)), funs(na_if(., 88))) %>%
  mutate_at(vars(everything(.)), funs(na_if(., 99))) %>%
  mutate(
    male = 2 - .$gender,
    age = 2021 - .$year_birth,
    res_vienna = recode(.$county, `8` = 1L, .default = 0L,),
    born_aus = 2 - .$born_aus,
    employment_fac = factor(.$employment, 
                           labels = c("Unselbststaendig erwerbstaetig (auch Lehrling), Privatwirtschaft", 
"Unselbststaendig erwerbstaetig (auch Lehrling), Oeffentlicher Dienst",
"Selbststaendig erwerbstaetig",
"Arbeitslos",
"Pensionist*in",
"Ausschliesslich haushaltsfuehrend",
"Schueler/in, Student/in, Bildungskarenz",
"Sonstiges (Dauerhaft arbeitsunfaehig oder Praesenz-/Zivildiener)",
"In Elternkarenz")),
    edu_fac = factor(.$edu,
                     labels = c("Volksschule oder weniger", 
                                "Hauptschule oder AHS Unterstufe",
                                "Polytechnikum, BMS (Fachschule, z.B. HASCH)",
                                "Lehre, Berufsschule",
                                "AHS mit Matura",
                                "BHS mit Matura (z.B. HTL, HAK, HBLA etc.)",
                                "Hochschulverwandte Lehranstalt oder Kolleg",
                                "Bachelor",
                                "Magister / Master / Diplomingenieur / Fachhochschule",
"Doktor / PhD")))
```

@@

```{r}
# recode such that higher values imply more strenght / align with wording
d_long %<>% 
  mutate_at(vars(med_txt_kro:med_vid_pri, health, sat_dem), 
            funs(recode(., `1` = 5L, `2` = 4L, `3` = 3L, `4` = 2L, `5` = 1L))) %>% 
  mutate_at(vars(loc_cntrl_int_1:loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L))) %>% 
  mutate_at(vars(born_aus_prnts), 
            funs(recode(., `3` = 0L, `2` = 2L, `1` = 1L)))

@@

Create mean values for each person, and unique changes per wave

```{r}
d_long %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_4), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

@@

@@

# measures
## life satisfaction

```{r}
model_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long)
fig_life_sat <- make_graph(model_life_sat, "Life satisfaction", ll = 0, ul = 10)
fig_life_sat
```

## positive affect

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long)
fig_aff_pos <- make_graph(model_aff_pos, "Positive affect", ll = 1, ul = 5)
fig_aff_pos
```

## negative affect

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long)
fig_aff_neg <- make_graph(model_aff_neg, "Negative affect", ll = 1, ul = 5)
fig_aff_neg
```

## Social media reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long)
fig_soc_med_read <- make_graph(model_soc_med_read, "Social Media Reading", ll = 1, ul = 5)
fig_soc_med_read
```

## Social media liking & sharing

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long)
fig_soc_med_like_share <- make_graph(model_soc_med_like_share, "Soc. Media Like & Share", ll = 1, ul = 5)
fig_soc_med_like_share
```

## Social media posting

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_post)
fig_soc_med_post <- make_graph(model_soc_med_post, "Social Media Posting", ll = 1, ul = 5)
fig_soc_med_post
```

@@

Save everything as a figure

```{r}
fig_desc <- grid.arrange(fig_life_sat, fig_aff_pos, fig_aff_neg, 
                         fig_soc_med_read, fig_soc_med_like_share, fig_soc_med_post,
                         nrow = 2)
ggsave("figures/fig_descriptives.pdf", 
       width = 7, height = 5,
       plot = fig_desc)
```

@@

```{r}
model_1 <- lmerTest::lmer(life_sat ~ (1 | id) + soc_med_read + soc_med_like_share + soc_med_post + soc_med_fb + soc_med_ig + soc_med_wa + soc_med_yt + soc_med_tw,
                data = d_long)
summary(model_1)
```

Now with diff. between within and between effects.

```{r}
model_2 <- lmerTest::lmer(life_sat ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w,
                data = d_long)
summary(model_2)
```

Now with control variables

```{r}
model_life_sat_lmer <- lmerTest::lmer(life_sat ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w + age + male + edu + born_aus + born_aus_prnts + res_vienna + edu + acc_bal + acc_gar + employment_fac
# + health_b + act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b + sat_dem_b + hh_income_b + med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + med_vid_orf_b + med_vid_pri_b + risk_prop_b + loc_cntrl_int_1_b + loc_cntrl_int_2_b + loc_cntrl_int_3_b + loc_cntrl_int_4_b + health_w + act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + sat_dem_w + hh_income_w + med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + med_vid_orf_w + med_vid_pri_w + risk_prop_w + loc_cntrl_int_1_w + loc_cntrl_int_2_w + loc_cntrl_int_3_w + loc_cntrl_int_4_w
,
                data = d_long)
summary(model_life_sat_lmer)
```

@@

```{r}
model_aff_pos_lmer <- lmerTest::lmer(aff_pos_m ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w  + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w + age + male + edu + born_aus + born_aus_prnts + res_vienna + edu + acc_bal + acc_gar + employment_fac
# + health_b + act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b + sat_dem_b + hh_income_b + med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + med_vid_orf_b + med_vid_pri_b + risk_prop_b + loc_cntrl_int_1_b + loc_cntrl_int_2_b + loc_cntrl_int_3_b + loc_cntrl_int_4_b + health_w + act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + sat_dem_w + hh_income_w + med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + med_vid_orf_w + med_vid_pri_w + risk_prop_w + loc_cntrl_int_1_w + loc_cntrl_int_2_w + loc_cntrl_int_3_w + loc_cntrl_int_4_w
,
                data = d_long)
summary(model_aff_pos_lmer)
```

@@

```{r}
model_aff_neg_lmer <- lmerTest::lmer(aff_neg_m ~ (1 | id) + (1 | wave) + soc_med_read_b + soc_med_read_w + soc_med_like_share_b + soc_med_like_share_w + soc_med_post_b + soc_med_post_w + soc_med_fb_b + soc_med_fb_w + soc_med_ig_b + soc_med_ig_w + soc_med_wa_b + soc_med_wa_w + soc_med_yt_b + soc_med_yt_w + soc_med_tw_b + soc_med_tw_w + age + male + edu + born_aus + born_aus_prnts + res_vienna + edu + acc_bal + acc_gar + employment_fac
# + health_b + act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b + sat_dem_b + hh_income_b + med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + med_vid_orf_b + med_vid_pri_b + risk_prop_b + loc_cntrl_int_1_b + loc_cntrl_int_2_b + loc_cntrl_int_3_b + loc_cntrl_int_4_b + health_w + act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + sat_dem_w + hh_income_w + med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + med_vid_orf_w + med_vid_pri_w + risk_prop_w + loc_cntrl_int_1_w + loc_cntrl_int_2_w + loc_cntrl_int_3_w + loc_cntrl_int_4_w
,
                data = d_long)
summary(model_aff_neg_lmer)
```

@@

Active vs. Passive

>>>>

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    # code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = T, 
                      tidy=T, dev = 'pdf', cache.extra = knitr::rand_seed)
options(digits = 3, width = 140, scipen=999)
```

@@

# define packages
packages <- c("brms", "corrplot", "devtools", "GGally", "ggplot2", 
              "gridExtra", "haven", "kableExtra", "knitr", 
              "lavaan", "lme4", "magrittr", "mice", "MVN", "PerFit", 
              "psych", "quanteda.textstats",
              "pwr", "semPlot", "semTools", "tidyverse")

@@

Extract characteristics from fitted lmer models.

```{r}
get_specs <- function(model){
    # Get mean, max, and min values

    dat <- coefficients(model)$wave
    specs <- data.frame(
    sd = attr(VarCorr(model), "sc"),
    min = min(dat),
    max = max(dat),
    mean = mean(dat$`(Intercept)`)
  )
}
```

Get data from fitted lmer objects

```{r}
get_dat <- function(model){
  coefficients(model)$wave %>% 
  tibble::rownames_to_column("wave") %>% 
  rename(value = "(Intercept)") %>% 
  mutate(wave = as.integer(.$wave),
         value = as.numeric(.$value)) 
} 
```

@@

```{r}
make_graph <- function(model, title, ll, ul, line = FALSE, labels = FALSE, lmer=TRUE, legend=TRUE){

    if(isTRUE(lmer)){
      dat <- get_dat(model)
    } else{
    dat <- model
  }

  graph <- 
    ggplot(dat, aes(wave, value, color = dimension)) +
    {if(legend) theme(
      legend.position = c(0.85, 0.8),
      legend.title = element_blank()
      )} + 
    {if(!legend) theme(
      legend.position = "none"
    )} +
    theme(axis.title.x=element_blank()) +
    coord_cartesian(ylim = c(ll, ul)) +
    ggtitle(title) +
    {if(line) geom_smooth(se = FALSE, method = 'loess')} +
    # geom_point() +
    scale_color_manual(values=c("dodgerblue3", "deepskyblue2", "magenta2", "green2", "red"))
  graph
}
```

@@

```{r}
make_graph_res <- function(data, sesoi = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                lwd = .75, height = .2
                , position = position_dodge(.6)
                ) +
  geom_point(size = 2
             , position = position_dodge(.6)
             ) +
  {if(sesoi) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(sesoi) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
  {if(sesoi) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} + 
  {if(sesoi) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

```{r}
doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
d_raw <- read_csv("data/10094_da_de_v4_0.csv")
```

@@

```{r}
d_wide %<>%
  mutate_at(vars(everything(.)), funs(na_if(., 88))) %>%
  mutate_at(vars(everything(.)), funs(na_if(., 99))) %>%
  mutate(
    male = 2 - .$gender,
    age = 2021 - .$year_birth,
    res_vienna = recode(.$county, `8` = 1L, .default = 0L,),
    born_aus = 2 - .$born_aus,
    home_owner = 2 - .$home_owner,
    employment_fac = factor(.$employment, 
                           # labels = c("Unselbststaendig erwerbstaetig (auch Lehrling), Privatwirtschaft",
                           #            "Unselbststaendig erwerbstaetig (auch Lehrling), Oeffentlicher Dienst",
                           #            "Selbststaendig erwerbstaetig",
                           #            "Arbeitslos",
                           #            "Pensionist*in",
                           #            "Ausschliesslich haushaltsfuehrend",
                           #            "Schueler/in, Student/in, Bildungskarenz",
                           #            "Sonstiges (Dauerhaft arbeitsunfaehig oder Praesenz-/Zivildiener)",
                           #            "In Elternkarenz")
                           labels = c("Employed industrie",
                                      "Employed public service",
                                      "Self-employed",
                                      "Unemployed",
                                      "Retired",
                                      "Housekeeping",
                                      "Student",
                                      "Incapacitated",
                                      "Parental Leave")
                           ),
    edu_fac = factor(.$edu,
                     # labels = c("Volksschule oder weniger", 
                     #            "Hauptschule oder AHS Unterstufe",
                     #            "Polytechnikum, BMS (Fachschule, z.B. HASCH)",
                     #            "Lehre, Berufsschule",
                     #            "AHS mit Matura",
                     #            "BHS mit Matura (z.B. HTL, HAK, HBLA etc.)",
                     #            "Hochschulverwandte Lehranstalt oder Kolleg",
                     #            "Bachelor",
                     #            "Magister / Master / Diplomingenieur / Fachhochschule",
                     #            "Doktor / PhD"),
                     labels = c("No degree", 
                                "Middle school",
                                "Vocational school",
                                "Technical school",
                                "High school",
                                "Applied high school",
                                "State college",
                                "Bachelor",
                                "Master",
                                "PhD")
                     ))
```

@@

```{r}
# recode such that higher values imply more strength / align with wording
d_long %<>% 
  mutate_at(vars(med_txt_kro:med_vid_pri, health, sat_dem, soc_med_fb:soc_med_post), 
            funs(recode(., `1` = 5L, `2` = 4L, `3` = 3L, `4` = 2L, `5` = 1L))) %>% 
  mutate_at(vars(loc_cntrl_int_1:loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L))) %>% 
  mutate_at(vars(born_aus_prnts), 
            funs(recode(., `3` = 0L, `2` = 2L, `1` = 1L)))

@@

@@

Create mean values for each person (between), and unique changes per wave (within).

```{r}
d_long %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_4, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

@@

# measures
## well-being
### life satisfaction

```{r}
model_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long)
summary(model_life_sat)
```

### positive affect

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long)
summary(model_aff_pos)
```

### negative affect

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long)
summary(model_aff_neg)
```

## Social media use
### reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_read)
```

### liking & sharing

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_like_share)
```

### posting

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_post)
```

## Social media channels
### Facebook

```{r}
model_soc_med_fb <- lmer(soc_med_fb ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_fb)
```

### Twitter

```{r}
model_soc_med_tw <- lmer(soc_med_tw ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_tw)

# Bayesian Approach
# model_soc_med_tw <- brm(soc_med_tw ~ (1 | id) + (1 | wave), d_long
# Also throws a warning
# model_soc_med_tw <- brm(soc_med_tw ~ (1 | id) + (1 | wave), d_long, control=list(adapt_delta=0.82))
# Currently doesn't work, likely for lack of memory
```

Interestingly, lme4 throws a warning, likely because there is too little variance across waves, while little variation measure itself. Let's inspect the raw means.

```{r}
soc_med_tw_m <- d_long %>% group_by(wave) %>% summarise(value = mean(soc_med_tw, na.rm = T))
soc_med_tw_m
```

Inspecting the means shows that the data are intact, only that the estimation didn't fully work.

### Instagram

```{r}
model_soc_med_ig <- lmer(soc_med_ig ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_ig)
```

### WhatsApp

```{r}
model_soc_med_wa <- lmer(soc_med_wa ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_wa)
```

### YouTube

```{r}
model_soc_med_yt <- lmer(soc_med_yt ~ (1 | id) + (1 | wave), d_long)
summary(model_soc_med_yt)
```

@@

Display the results in a combined figure.

```{r}
fig_desc_dat <- data.frame(
  rbind(
    data.frame(type = "Life satisfaction", dimension = "Life satisfaction", get_dat(model_life_sat)),
    data.frame(type = "Affect", dimension = "Positive", get_dat(model_aff_pos)),
    data.frame(type = "Affect", dimension = "Negative", get_dat(model_aff_neg)),
    data.frame(type = "Social media use", dimension = "Reading", get_dat(model_soc_med_read)),
    data.frame(type = "Social media use", dimension = "Liking & Sharing", get_dat(model_soc_med_like_share)),
    data.frame(type = "Social media use", dimension = "Posting", get_dat(model_soc_med_post)),
    data.frame(type = "Social media channel", dimension = "Facebook", get_dat(model_soc_med_fb)),
    data.frame(type = "Social media channel", dimension = "Twitter", get_dat(model_soc_med_tw)),
    data.frame(type = "Social media channel", dimension = "Instagram", get_dat(model_soc_med_ig)),
    data.frame(type = "Social media channel", dimension = "WhatsApp", get_dat(model_soc_med_wa)),
    data.frame(type = "Social media channel", dimension = "YouTube", get_dat(model_soc_med_yt))
  ) %>% 
    mutate(
      type = factor(.$type, levels = c("Life satisfaction", "Affect", "Social media use", "Social media channel")),
      dimension = factor(.$dimension, levels = c("Life satisfaction", "Positive", "Negative", "Reading", "Liking & Sharing", "Posting", "Facebook", "Twitter", "Instagram", "WhatsApp", "YouTube"))
      )
)

fig_desc_life_sat <- make_graph(
  fig_desc_dat %>% filter(type == "Life satisfaction"), 
  title = "Life satisfaction", 
  ll = 0, ul = 10, 
  lmer = FALSE, 
  line = TRUE,
  legend = FALSE
  )

fig_desc_aff <- make_graph(
  fig_desc_dat %>% filter(type == "Affect"), 
  title = "Affect", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc_soc_med_use <- make_graph(
  fig_desc_dat %>% filter(type == "Social media use"), 
  title = "Social media use", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc_soc_med_channel <- make_graph(
  fig_desc_dat %>% filter(type == "Social media channel"), 
  title = "Social media channel", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE
  )

fig_desc <- grid.arrange(fig_desc_life_sat, fig_desc_aff, 
                         fig_desc_soc_med_use, fig_desc_soc_med_channel,
                         nrow = 2, ncol = 2)

ggsave("figures/fig_descriptives.pdf", 
       width = 10, height = 6,
       plot = fig_desc)
```

## table

```{r}
tab_desc_dat <- rbind(
    "Life satisfaction" = get_specs(model_life_sat),
    "Positive affect" = get_specs(model_aff_pos),
    "Negative affect" = get_specs(model_aff_neg),
    "Read" = get_specs(model_soc_med_read),
    "Like & share" = get_specs(model_soc_med_like_share),
    "Posting" = get_specs(model_soc_med_post),
    "Facebook" = get_specs(model_soc_med_fb),
    "Twitter" = c(sd = get_specs(model_soc_med_tw)$sd,
                  min = min(soc_med_tw_m$value, na.rm = TRUE),
                  max = max(soc_med_tw_m$value, na.rm = TRUE),
                  mean = mean(soc_med_tw_m$value, na.rm = TRUE)
                  ),
    "Instagram" = get_specs(model_soc_med_ig),
    "WhatsApp" = get_specs(model_soc_med_wa),
    "YouTube" = get_specs(model_soc_med_yt)
    )
```

@@

First, without control variables.

```{r}
model_life_sat_lmer_nco <- lmerTest::lmer(life_sat ~ 
                            (1 | id) + (1 | wave) + 
                            soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                            soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                            soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                            soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b,
                data = d_long)
summary(model_life_sat_lmer_nco)
```

Now with control variables.

```{r}
model_life_sat_lmer <- lmerTest::lmer(life_sat ~
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        # hh_income_b + # large dropout (900 obs)
                                        # hh_adults + # too much dropout
                                        # hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner + 
                                        # home_owner + # too much dropout
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_life_sat_lmer)
```

```{r}
# + health_b + act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b + sat_dem_b + hh_income_b + med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + med_vid_orf_b + med_vid_pri_b + risk_prop_b + loc_cntrl_int_1_b + loc_cntrl_int_2_b + loc_cntrl_int_3_b + loc_cntrl_int_4_b + health_w + act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + sat_dem_w + hh_income_w + med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + med_vid_orf_w + med_vid_pri_w + risk_prop_w + loc_cntrl_int_1_w + loc_cntrl_int_2_w + loc_cntrl_int_3_w + loc_cntrl_int_4_w
```

@@

First, without control variables.

```{r}
model_aff_pos_lmer_nco <- lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
                                      , data = d_long)
summary(model_aff_pos_lmer_nco)
```

Now with control variables.

```{r}
model_aff_pos_lmer <- lmerTest::lmer(aff_pos_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        # hh_income_b + # large dropout (900 obs)
                                        # hh_adults + # too much dropout
                                        # hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner + 
                                        # home_owner + # too much dropout
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_aff_pos_lmer)
```

@@

First, without control variables.

```{r}
model_aff_neg_lmer_nco <- lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b
                                      , data = d_long)
summary(model_aff_neg_lmer_nco)
```

Then, with control variables.

```{r}
model_aff_neg_lmer <- lmerTest::lmer(aff_neg_m ~ 
                                        (1 | id) + (1 | wave) + 
                                        soc_med_read_w + soc_med_like_share_w + soc_med_post_w + 
                                        soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
                                        soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
                                        soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
                                        age + male + born_aus + born_aus_prnts + edu_fac + employment_fac + health_b + 
                                        res_vienna + acc_bal + acc_gar + home_sqm + 
                                        # hh_income_b + # large dropout (900 obs)
                                        # hh_adults + # too much dropout
                                        # hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + hh_oldfam + hh_outfam + hh_partner + 
                                        # home_owner + # too much dropout
                                        med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
                                        med_vid_orf_b + med_vid_pri_b + 
                                        risk_prop_b + loc_cntrl_int_m_b + 
                                        act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
                                        act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
                                        sat_dem_w + sat_dem_b 
                                      , data = d_long)
summary(model_aff_neg_lmer)
```

@@

First, extract data.
